---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multiprobit

<!-- badges: start -->
<!-- badges: end -->

The goal of multiprobit is to perform fast Bayesian inference for multivariate probit models. The method uses a latent Gaussian variable parameterisation of the correlation matrix, and numerical optimisation and integration to find the posterior distributions of the model coefficients and correlation matrix.

## Installation

<!--
You can install the released version of `multiprobit` from [CRAN](https://CRAN.R-project.org) with:

```{r eval = FALSE}
install.packages("multiprobit")
```
-->

To install the development version of `multiprobit` from github, use
```{r eval = FALSE}
remotes::install_github("finnlindgren/multiprobit", ref = "devel")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(multiprobit)
## basic example code
```

