---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multiprobit

<!-- badges: start -->
[![R build status](https://github.com/finnlindgren/multiprobit/workflows/R-CMD-Check/badge.svg)](https://github.com/finnlindgren/multiprobit/actions)
[![R code coverage status](https://github.com/finnlindgren/multiprobit/workflows/test-coverage/badge.svg)](https://github.com/finnlindgren/multiprobit/actions)
[![Codecov test coverage](https://codecov.io/gh/finnlindgren/multiprobit/branch/master/graph/badge.svg)](https://codecov.io/gh/finnlindgren/multiprobit?branch=devel)
<!-- badges: end -->

The goal of multiprobit is to perform fast Bayesian inference for multivariate probit models. The method uses a latent Gaussian variable parameterisation of the correlation matrix, and numerical optimisation and integration to find the posterior distributions of the model coefficients and correlation matrix.

## Installation

<!--
You can install the released version of `multiprobit` from [CRAN](https://CRAN.R-project.org) with:

```{r eval = FALSE}
install.packages("multiprobit")
```
-->

To install the development version of `multiprobit` from github, use
```{r eval = FALSE}
remotes::install_github("finnlindgren/multiprobit", ref = "devel")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
if (interactive()) {
  library(multiprobit)
  
  N <- 6
  d <- 2
  J <- 2
  
  set.seed(1L)
  X <- cbind(1, matrix(rnorm(N * (J - 1)), N, J - 1))
  B <- matrix(0.5, J, d)
  Y <- matrix(rnorm(N * d, mean = as.vector(X %*% B)) > 0, N, d)
  df <- d + 1
  prec_beta <- 0.1
  
  model <- mp_model(response = Y, X = X,
                    df = df, prec_beta = prec_beta)
  opt <- multiprobit(model = model,
                     options =
                       mp_options(
                         gaussint = list(max.threads = 1),
                         strategy = "stepwise"))
}
```
